Data-Centric Recommender System for Tackling Selection Bias-induced Distribution Shift

### 2022-08-09 paper/paper.tex
Finish drafting stage 2 experiments
Run experiment

% ready for submission
\usepackage{neurips_2022}

@@

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2022}

@@

\title{Propensity Estimation Matrix Factorization Through Mixed-Quantized Dataset}

@@

\author{%
  David S.~Hippocampus\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

>>>>

% ready for submission
% \usepackage{neurips_2022}

@@

% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage[preprint]{neurips_2022}

@@

\title{Data-Centric Recommender System for Tackling Selection Bias-induced Distribution Shift}

@@

\author{%
  Fengyu Li \\
  Cornell University\\
  \texttt{fl334@cornell.edu} \\
  \And
  Sarah Dean \\
  Cornell University \\
  \texttt{sdean@cornell.edu} \\
}
